WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-07-06 ms.tex
Rearrange figures
Add autocorrelation likelihood plot

>>>>

\begin{figure*}
    \includegraphics[width=\textwidth]{autocorr-likelihood}
    \caption{\label{fig:autocorr-likelihood}The autocorrelation likelihood for a $(1.4, 1.4)$\,$M_\odot$ binary as observed by four detector configurations: from top to bottom, the final sensitivity achieved by the \acs{LIGO} Hanford, \acs{LIGO} Livingston, and Virgo detectors in their ``initial'' configuration, and the final Advanced \acs{LIGO} design sensitivity. The left panels show the noise amplitude spectral densities. The middle panels show the absolute value of the autocorrelation function. The right panel shows the phase-marginalized autocorrelation likelihood for \ac{SNR}=1,~2,~4,~and~8. In the right panel, the time scale is normalized by \ac{SNR} so that one can see that as \ac{SNR} increases, a central parabola is approached (the logarithm of a Gaussian distribution with standard deviation given by the Fisher matrix).}
\end{figure*}
